\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-26 Manuscript/supp.tex

\section{Rank-Based Comparison with Pooled Men and Women Data}

@@

\section{GAMLSS Results for Women Data}
We can repeat our reaction time barrier analysis described in section 3.2, but
fit the same model to women's data from 2001 to 2023.  Once again we utilize
the power of the venue effect within $\mu$ and a heat effect within $\sigma$. 
We visualize the data we are analyzing in Figure~\ref{fig:WomensBoxplot}.
Similar to the men's data, reaction times from 2022 appear lower than in other
years.

@@

>>>>

\section{Rank-Based Comparison with Pooled Data}

@@

\section{GAMLSS Results for Women Data}

We can repeat our reaction time barrier analysis described in section 3.2, but
fit the same model to women's data from 2001 to 2023.  Once again we utilize
the power of the venue effect within $\mu$ and a heat effect within $\sigma$. 
We visualize the data we are analyzing in Figure~\ref{fig:WomensBoxplot}.
Similar to the men's data, reaction times from 2022 appear lower than in other
years.

@@

The results are slightly different from those from the men's data,
which echoes existing studies reporting gender differences in reaction
times \citep[e.g.,][]{lipps2011implications, babicc2009reaction,
  panoutsakopoulos2020gender}.
